---
title: "Exercise quality prediction"
author: "Krisztian Papp"
date: "October 7, 2018"
output: html_document
---

# Aim:

The goal is predicting the quality of dumbell excercise useing data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants.

## Data cleaning
The data come from: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har.
Load 'train' and 'test' dataset.
```{r message=FALSE, warning=FALSE}
library(readr)
train<-read_csv("pml-training.csv")
test<-read_csv(file="pml-testing.csv")
```

I remove following variables:
 * contains mainly NA-s
 * contains only the ID

```{r}
s<-colSums(apply(train, 2, is.na))
plot(s, ylab = "Number of NA or empty cells", xlab="Variables", main = "Many variables contains mainly NA-s")
keep_variables<-s<5000
keep_variables[1]<-FALSE
train<-train[,keep_variables]
sr<-colSums(apply(train, 1, is.na))
train<-train[sr==0,]
train<-train
test<-test[,keep_variables]
```

The clean dataset contains ony 58 varables, I will use only these in further analysis.

Create "training" and "testing" datasets from the 'train' dataset:

* Randomly choose 70% of 'train' dataset for training, and the leftover to calculate the of-sample error

```{r message=FALSE}
library(caret)
library(rattle)
set.seed(555)
inTrain<-createDataPartition(y=train$classe, p=0.7, list=FALSE)
training<-train[inTrain,]
testing<-train[-inTrain,]
```

Fit a random forest model to the 'training' dataset
```{r message=FALSE}
fitm<-train(classe~., method="rf", data=training)
fitm
```
* I used the "rf" method, as the "rpart" gave very poor result


On "testing" dataset the out-of sample error is the following:
```{r}
pred<-predict(fitm, newdata = testing)
confusionMatrix(as.factor(pred), as.factor(testing$classe))
```

Finally predit the "test" set classes:

```{r}
pred1<-predict(fitm, newdata = test)
pred1
```

